WDIAS : A Microservices-Based Weather Data Integration and Assimilation System\\

### 2020-05-07 Thesis.tex
Updates from Overleaf

\usepackage{hyperref} %%% \hl{} on sections will fail this
\usepackage[noabbrev,capitalise]{cleveref}

@@

        %\vfill
       \vspace{72pt}
        \large
        Department of Computer Science and Engineering\\
        \vspace{24pt}
        University of Moratuwa\\
        Sri Lanka\\
        \vspace{32pt}
        March 2020

@@

\vspace{0.5in}
\noindent
\begin{tabu} to 1.0\textwidth { X[l] X[l] }
  Signature: & Date:
\end{tabu}

@@

\vspace{0.5in}
\noindent
\begin{tabu} to 1.0\textwidth { X[l] X[l] }
  Name of the supervisor: & Dr. HMN Dilum Bandara\\ [1.5ex]
  Signature of the supervisor: & Date:
\end{tabu}

@@

\import{results/}{sec_2-workload.tex}

\import{results/}{sec_3-observations.tex}

>>>>

% \usepackage{hyperref} %%% \hl{} on sections will fail this
\usepackage[noabbrev,capitalise]{cleveref}

@@

        %\vfill
       \vspace{72pt}
        \large
        Department of Computer Science and Engineering\\
        \vspace{24pt}
        University of Moratuwa\\
        Sri Lanka\\
        \vspace{32pt}
        May 2020

@@

\vspace{0.5in}
\noindent
\begin{tabu} to 1.0\textwidth { X[6.5,l] X[3.5,l] }
  Signature: & Date:
\end{tabu}

@@

\vspace{0.5in}
\noindent
\begin{tabu} to 1.0\textwidth { X[6.5,l] X[3.5,l] }
  Name of the supervisor: & Dr. HMN Dilum Bandara\\ [2.5ex]
  Signature of the supervisor: & Date:
\end{tabu}

@@

% \import{results/}{sec_2-workload.tex}

% \import{results/}{sec_3-observations.tex}
